### 2020-02-17 paper/revisions/review-responses.tex

        		  We changed the paragraph as follows:\\
        		  During the depletion step, the core was maintained critical and total fuel mass was almost constant (dm $\leq$ 0.1\%). To determine the appropriate depletion step size, we conducted a time step refinement study. We started with $\Delta t=30$days and gradually increased the depletion time step until the error in $k_{eff}$ became significant. For $\Delta t=1$year the maximum change in $k_{eff}$ was $\leq$ 0.02\%), therefore we adopted a constant, 365-day-long time step for all simulation in this work.

        \end{solution}

        %---------------------------------------------------------------------
        \question During the molten salt reactor operation, part of fuel salt flows outside of reactor core then the fission reaction is not happened in external loop, however the decay reactions happens everywhere. In other words, during one burnup step, the fission reactions occur in only part of the time (depends on the ratio of time taken in fuel salt passing reactor core and external loop), and nuclides' decay or other reactions occur in the whole burnup step time. Have you considered this in SERPENT calculation?  
        \begin{solution}

		          Thank you for your insightful comment. We used total fuel 
		          salt inventory in the primary loop to define the fuel 
		          material in the SERPENT input. Moreover, we accordingly 
		          adjusted power density in SERPENT burnup calculations 
		          because fission takes place only in the core region.
		          We changed the paragraph as follows:\\

		          During the molten salt reactor operation, part of fuel salt flows outside of the reactor core then the fission reaction has not happened in the external loop, however, the decay reactions happen everywhere. We used total fuel salt inventory in the primary loop to define the fuel material in the SERPENT input. Moreover, we accordingly adjusted power density in SERPENT burnup calculations because fission takes place only in the core region.     
        \end{solution}

@@

        \begin{solution}
                Thank you very much for these comments. We appreciate your detailed review, which has certainly improved the paper. The manuscript has been enhanced and more detail is described regarding these changes in the specific comment responses below.
        \end{solution}

        %---------------------------------------------------------------------

        \question SD-TMSR concept development does not correctly described in the section "introduction", where it states that the SD-TMSR was introduced by the Chinese Academy of Sciences. Actually, SD-TMSR concept was proposed by ORNL as early as in the 1960s, which was called Molten salt breeding reactor (MSBR) (see Ref.: Tech. Rep. ORNL-4541). In addition, the study of reference 7 which was cited to illustrate SD-TMSR concept actually adopted the single-flow single-zone MSR rather than SD-TMSR.

        \begin{solution}
                 Thank you for catching this. The whole statement has been 
                 modified to read:\\

                 The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with a thermal power of 2,250
                 MW$_{th}$ was proposed for the first time by ORNL as early as in the 1960s, which was called Molten salt breeding reactor (MSBR) \cite{robertson_conceptual_1971}.

@@

                 Thank you for catching this. Reference 7 has been removed from the paragraph.

        \end{solution}

        %---------------------------------------------------------------------

        \question The authors did not conduct a sufficient literature survey on the fuel cycle transition studies for the SD-TMSR concept. Cui. et al., have made an extensive study on fuel cycle transition for SD-TMSR by employing LEU and Pu as the startup fissile materials and two transition modes (in-core transition and ex-core transition) (see Ref.: Transition toward thorium fuel cycle in a molten salt reactor by using plutonium, NUCL SCI TECH (2017) 28:152; Possible scenarios for the transition to thorium fuel cycle in molten salt reactor by using enriched uranium. Progress in Nuclear Energy 104 (2018) 75-84). The state "For the SD-TMSR concept, simulating the fissile core startup and fuel cycle transition with other fissile materials (except U-233) has not studied before" in page 3 is therefore inaccurate.
        \begin{solution}
                Thank you for your helpful review. The state "For the SD-TMSR 
                concept, simulating the fissile core startup and fuel cycle 
                transition with other fissile materials (except$^{233}$U) has 
                not studied before" in page 3, has been removed. 
                The following paragraphs have been added to the manuscript.\\

                Cui \emph{et al.} (2017-2018) analyzed the fuel transition from enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the MSBR-like design. Cui \emph{et al.} found that the fuel transition can be achieved by using: (1) enriched uranium with greater than 40\% enrichment, which rises the proliferation concerns; (2) Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel \cite{cui2017transition,cui2018possible}.

@@

               \begin{enumerate}
               	\item The simulation starts without injecting refueling materials (i.e. only removing FPs and Pa).
               	\item After the first depletion calculation step, we check the total mass density of FPs and Pa in the \texttt{FP-waste tank} and \texttt{Pa-decay tank}, respectively.
               	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
               	\subitem 3a. \textbf{Thorium feed mechanism}: mass of injected $^{233}$U $\approx$ mass of extracted Pa and mass of injected Th $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
               	\subitem 3b. \textbf{Non-thorium feed mechanism}: mass of injected $^{233}$U $\approx$ mass of extracted Pa and mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
               	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant (1/s).
               \end{enumerate}
               In both feed mechanisms (thorium and non-thorium) we continuously added $^{233}$U and the mass of injected $^{233}$U is equal to the mass of extracted Pa ($^{233}$Pa decays to $^{233}$U after $\approx$ 27 d). To keep the total fuel mass almost constant, for \textbf{thorium feed mechanism}, the mass of injected Th must be equal to the mass of extracted FPs and for \textbf{non-thorium feed mechanism}, the mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) must be equal to the mass of extracted FPs.

        \end{solution}

        %--------------------------------------------------------------------

        \question Phenomenons presented in Figure 3 that K-eff for the case of Pu+HALEU firstly increases and then decreases, and the time to become subcritical for the case of reactor-grade Pu is longest (except the case of U-233) should be explained.
        \begin{solution}
                 Thank you for your insightful comment. Phenomenons presented 
                 in Figure 3 have been described in the manuscript.
                 The following paragraph has been added to the manuscript.\\

                 For Pu+HALEU case, $k_{eff}$ firstly increases during the first $\approx$ $3$ EFPY and then gradually decreases. This is due to the conversion of $^{238}$U from HALEU into fissile plutonium, which often produces the majority of the neutrons until the transition to Th/$^{233}$U fuel cycle. Figure~\ref{fig:diffPuAll811} shows the variation in fissile plutonium isotopes ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) inventory during reactor operation. For TRU and reactor-grade Pu, the fissile plutonium isotopes are gradually depleted, during operating (the fissile material is dominated by Pu in these cases). For HALEU case, the fissile material is dominated by $^{235}$U, however, $^{238}$U is converted into fissile plutonium. Therefore, the mass of fissile plutonium increases during operating but its value still relatively low. For Pu+HALEU case, the mass of the fissile plutonium isotopes increases within the first $\approx$ $3$ EFPY and then decreases. The reactivity from the produced Pu is much greater than the depletion of the initial reactivity (due to the depletion of initial fissile isotopes), consequently, $k_{eff}$ increases during the first $\approx$ $3$ years and then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is insufficient to maintain the reactor criticality and counteract neutron absorption in non-fissile isotopes.

                 The following paragraph has been added to the manuscript.\\

                 Figure~\ref{fig:keff1} shows that the decrease in $k_{eff}$ for reactor-grade Pu case occurs at the much later operating time than for other cases because the neutron spectrum in the reactor-grade Pu initial core is hardened; more $^{232}$Th is being converted to $^{233}$U. Nevertheless, this amount of the $^{233}$U is not enough to counteract the neutron absorption in the non-fissile Pu isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted.

@@

                  The following paragraph has been added to the manuscript.\\

                  The target is to maintain the core criticality for a long period of time without any external feed of $^{233}$U. Figure~\ref{fig:Keff_U2332} shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR. The fast extraction of Pa from the core (RP = $30$ $s$) leads to long operating time. Also, a relatively large amount of $^{233}$U can be obtained when we applied RP = $30$ $s$ against $10.59$ $d$. The RP equal to $10.59$ $d$ is not suitable for TRU and reactor-grade Pu cases because additional $^{233}$U was required to supply the core after startup. Therefore, we selected the RP = $30$ $s$. This produces $^{233}$U in the \texttt{Pa-decay tank} barely enough to operate the TRU-started SD-TMSR for a long period of time ($\approx$ 40 years). For reactor-grade Pu case, the produced $^{233}$U is sufficient to maintain the core criticality within the 60-years of operation (see Figure~\ref{fig:keff2}).
        \end{solution}

        %--------------------------------------------------------------------
        \question For Figure 9, it is inaccurate to state that the mass of U-233 reaches equilibrium after ~30 years, apparently from the figure, we can observe that the mass of U-233 for three of the cases still increase/decrease after 30 years.

        \begin{solution}
                Thank you for the excellent point. The statement has been removed from the text.
                Moreover, we rewrite the paragraph to address this thought:\\

                Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases. For $^{233}$U case, the mass of $^{233}$U increases with operating time and reaches $\approx$ $1.7$ $t$ at the EOL. For reactor-grade Pu and TRU cases, the mass of $^{233}$U firstly, increases and after $\approx$ $35$ and $45$ years for Pu and TRU cases, respectively, decreases. The neutron spectrum shift during operating affects the inventory of $^{233}$U in the fuel salt. Hard neutron spectrum converts more $^{233}$U from $^{232}$Th. For the reactor-grade Pu and TRU cases, during operating, the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope; the neutron spectrum softens (low conversation of $^{233}$U from $^{232}$Th). However, for $^{233}$U case, the neutron spectrum is hardened at EOL due to the accumulation of Pu isotopes.

@@

        \end{solution}

        %--------------------------------------------------------------------
        \question Regarding to Figure 10, reasons should be provided to explain why the time achieving Pu solubility limit for the case of TRU is shorter than that of the case of reactor-grade Pu.
        \begin{solution}
                 This has now been clarified in the text.
                 We rewrite the paragraph to address this thought:\\

                 Notably, for TRU case, the time achieving Pu solubility limit is shorter than that for reactor-grade Pu case. The reason for this is the relatively high concentration of Pu in the initial heavy metal for the TRU-started SD-TMSR ($\approx$ $29.26$ \% compared with $14.31$ \% for Pu-started SD-TMSR, see Table 5).

@@

        \end{solution}

        %--------------------------------------------------------------------
        \question It is hard to understand that the neutron spectrum of TRU case at BOL is softer than U-233 case since TRU has a greater amount of thermal neutron absorbers and the fissile material is dominated by Pu which would generate hard neutron spectrum.

        \begin{solution}
                 We appreciate your detailed review.                   
                 The following paragraph has been added to the manuscript:\\

                 The neutron spectrum of TRU case at BOL is softer than $^{233}$U case because $^{232}$Th inventory is much lower for the TRU case: $54.4$ $t$ instead of $76.9$ $t$ for the $^{233}$U. $^{232}$Th has a very high absorption cross section in the thermal region ($\approx10^2 $b). Moreover, $^{232}$Th has resonance region between $10^{-5}$ and $10^{-3}$ which justify relatively low energy of neutrons for the TRU case in this energy range (see Figure~\ref{fig:spectrumFLUX110vC}).

@@

        \end{solution}

        %--------------------------------------------------------------------
        \question More details should be provided to explain the radial 
        neutron flux distribution for the cases of Pu reactor-grade and TRU 
        presented in Fig.13 and 14. For both the radial fast and thermal 
        neutron flux change from BOL to EOL, why it is much larger for Pu 
        reactor-grade case compared with TRU case. In addition, the state "In 
        contrast, for the reactor-grade Pu and TRU cases, significant changes 
        are observed for thermal neutron flux in the outer core zone and 
        reactor" is inaccurate, apparently from Figure 14, it can be seen that 
        the Pu reactor-grade (initial) case has a small change in the outer 
        core zone and reflector. 
        \begin{solution}
				Thank you for pointing it out. Figure 14 shows significant 
				changes \textbf{during reactor operation} in the outer core 
				zone for the Pu (green line) and almost no changes for the TRU 
				(orange). In this paragraph, we comparing changes in the flux 
				due to fuel salt depletion (initial vs equilibrium), but not 
				with $r$ coordinate. However, we are agree that thermal flux 
				drop in the reflector is more dramatic for the TRU (initial 
				and equilibrium compositions) an the Pu (equilibrium) cases 
				than for the U-233 case. We think it happens because of 
				non-optimal geometry of the core for the Pu and TRU initial 
				loading.			
				The following paragraphs has been added to the manuscript for 
				clarify this point:\\

				Notably, the neutron flux change for both the fast and thermal 
				energies is 
				much larger for the reactor-grade Pu case than for TRU case 
				(Figures~15 and 16). The 
				reason is the 
				much softer neutron spectrum for the TRU initial loading 
				compared with the 
				reactor-grade Pu as shown in 
				Figure~14: peak thermal 
				neutron flux is about 4 times larger for the TRU case. The 
				neutron spectrum in 
				the SD-TMSR core initially loaded by TRU is much softer than 
				the reactor-grade 
				Pu case and even than the U-233 case because $^{232}$Th 
				inventory is the 
				lowest for the TRU case: 54.4t instead of 67.5t  and 76.9t for 
				the  
				reactor-grade Pu and U-233 cases, respectively 
				(Table~5). 
				$^{232}$Th greatly affects the neutron energy spectrum due to 
				its large 
				absorption cross section in the thermal energy range and 
				resonance region 
				between $10^{-5}$ and $10^{-3}$. Finally, when the TRU and the 
				reactor-grade 
				Pu cases reached equilibrium fuel salt composition ($\approx 
				30$ years after 
				startup), the radial fast and thermal neutron flux 
				distribution became similar 
				in both shape and magnitude.

				More changes in thermal neutron flux shape and magnitude 
				during the reactor 
				operation for the $^{233}$U case are observed in the inner 
				core zone 
				($R\lesssim150$) than in the outer core zone. In the outer 
				core zone, 
				significant changes during reactor operation are observed for 
				the thermal 
				neutron flux for the reactor-grade Pu case. In contrast, for 
				the TRU case, it 
				is almost negligible. Additionally, 
				Figure~16 shows 
				relatively significant changes in thermal flux leakage from 
				the core for the 
				Pu (equilibrium composition) and TRU (initial and equilibrium 
				composition) 
				cases. The SD-TMSR core design was optimized for $^{233}$U  
				\cite{li_optimization_2018}; thus, the core geometry (e.g., 
				channels lattice 
				pitch) must be re-optimized for another type of fuel to obtain 
				better 
				neutronics performance.
        \end{solution}

        %--------------------------------------------------------------------
        \question Regarding to the FTC for three different cases, reasons should be provided to explain why spectrum softening will positively affects the FTC since generally harder neutron spectrum would benefit FTC.
        \begin{solution}
                Thank you for your insightful comment.  Indeed, the Doppler 
                effect coefficient ($\alpha_{D,F}$) is usually stronger for 
                harder spectrum (see Table~8, ``Fuel salt temperature''), so, 
                spectrum softening negatively affects $\alpha_{D,F}$ (it is 
                decreasing by value but still negative). But we additionally 
                considered the fuel salt density coefficient 
                ($\alpha_{\rho,F}$), which is usually positive in thermal MSRs 
                (e.g., $+1.09pcm/K$ for the \gls{MSBR}           
                \cite{robertson_conceptual_1971}) and \textbf{softer} neutron 
                spectrum benefit $\alpha_{\rho,F}$ \cite{li_effects_2018-1, 
                rykhlevskii2019modeling}. More analysis on this topic:
            Li, X., Ma, Y., Yu, C. et al. Effects of fuel salt composition on 
            fuel salt temperature coefficient (FSTC) for an under-moderated 
            molten salt reactor (MSR). NUCL SCI TECH 29, 110 (2018). 
            https://doi.org/10.1007/s41365-018-0458-1.     
	            The following paragraphs has been added to the manuscript:\\

	            The \gls{FTC} is a combination of the Doppler effect 
	            coefficient 
	            ($\alpha_{D,F}$) and density coefficient ($\alpha_{\rho,F}$) 
	            and significantly 
	            affected by the neutron spectrum. Li \emph{et al.} reported 
	            that 
	            $\alpha_{D,F}$ in thermal \gls{MSR} is always negative and 
	            increases by 
	            magnitude when spectrum hardening (see Table~8, first raw). 
	            In contrast, $\alpha_{\rho,F}$ is a combination of 
	            moderator-to-fuel volume 
	            ratio, absorption cross section of heavy metal, and the core 
	            leakage. When the 
	            fuel salt temperature increases, the salt becomes less dense, 
	            causing a 
	            reduction in the fuel concentration and the neutron spectrum 
	            become softer. 
	            Such spectrum softening is leading to a rise in macroscopic 
	            absorption cross 
	            section of the fissile isotopes. Moreover, the spectrum 
	            softening may leads to 
	            a larger fast fission reaction rate \cite{li_effects_2018-1}. 
	            Thus, spectrum 
	            softening positively affects the density coefficient 
	            ($\alpha_{\rho,F}$): 
	            $+1.54$ $pcm/K$ and $-1.58$ $pcm/K$ at the startup and 
	            equilibrium for the 
	            reactor-grade Pu case, respectively. More discussion about 
	            effects of fuel 
	            salt composition in the \gls{FTC} can be found elsewhere 
	            \cite{li_effects_2018-1}.
        \end{solution}

### 2020-02-17 paper/revisions/review-responses.tex

        %--------------------------------------------------------------------
        \question It seems unclear why (what is the purpose) to conduct the study of six factor analysis.
        \begin{solution}
                 Thank you for bringing our attention to the point. Usually, 
                 six factor analysis helps to understand reasons of changes in 
                 TCs and control rod worths during reactor operation. But in 
                 this case, considering many various cases, such analysis is 
                 outmoded.           
                  The section has been removed from the manuscript completely.
        \end{solution}

### 2020-02-17 paper/results.tex
Reviewer 2 comments 9-11 addressed #47 #38

\subsection{Neutron flux}
Figures~\ref{fig:fast_flux} and \ref{fig:thermal_flux} show the radial 
distribution of fast (energy range between 0.625 eV and 20 MeV) and thermal 
(energy range between 10$^{-5}$ eV and 0.625 eV) neutron flux for three 
different initial fissile materials in the fuel salt ($^{233}$U, reactor-grade 
Pu, TRU) at startup and at equilibrium (after $\approx 30$ years of 
operation). Actinides' evolution and poisonous fission product accumulation 
for various initial fissile compositions demonstrates the different effects on 
the SD-TMSR neutronics performance. For the $^{233}$U case, the thermal 
neutron flux is suppressed at equilibrium because fissile $^{233}$U in the 
core is being substituted with heavier fissile actinides: $^{235}$U, 
$^{239}$Pu, and $^{241}$Pu. This agrees with results in literature 
\cite{rykhlevskii2019modeling, ashraf2019whole_core}.
\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
	\includegraphics[width=\textwidth]{radial_fast_flux_init_vs_eq.png} 
	\caption{Radial fast neutron flux distribution for 3 different initial 
		fuel salt compositions at startup and equilibrium (the fast flux 
		confidence interval $\pm\sigma<2.5$\% for all cases).}
	\label{fig:fast_flux}
\end{figure}

Opposite behavior is observed for the reactor-grade Pu and TRU cases. For  
these cases, the thermal neutron flux increases during operation while fast 
neutron flux decreases. Fissile Pu nuclides (generate relatively hard 
spectrum) from initial fuel salt composition are gradually substituted with  
$^{233}$U (generates relatively soft spectrum), produced from fertile 
$^{232}$Th. During reactor operation, $^{233}$U becomes the primary fissile 
isotope, which softening the neutron spectrum of the reactor. 
\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
	\includegraphics[width=\textwidth]{radial_thermal_flux_init_vs_eq.png} 
	\caption{Radial thermal neutron flux distribution for 3 different initial 
		fuel salt compositions at startup and equilibrium (the thermal flux 
		confidence interval $\pm\sigma<1.6$\% for all cases).}
	\label{fig:thermal_flux}
\end{figure}

More changes in thermal neutron flux shape and magnitude for the 
$^{233}$U case are observed in the inner core zone ($R\lesssim150$) than 
in the outer core zone. In contrast, for the reactor-grade Pu and TRU cases, 
significant changes are observed for thermal neutron flux in the outer core 
zone and reflector. Additionally, Figure~\ref{fig:thermal_flux} shows 
relatively large changes in thermal flux leakage from the core for the Pu and 
TRU cases. The SD-TMSR core design was optimized for $^{233}$U  
\cite{li_optimization_2018}, thus, the core geometry (e.g., channels lattice 
pitch) must be re-optimized for another type of fuel to obtain better 
neutronics performance.

@@

The \gls{FTC} is negative for all considered fuel compositions due to thermal 
Doppler broadening of the resonance capture cross sections in the thorium. For 
the $^{233}$U case, the \gls{FTC} decreases in magnitude by $25\%$ due to 
neutron spectrum hardening during the reactor operation. For reactor-grade Pu 
and TRU cases, the \gls{FTC} increases in magnitude at equilibrium, by $31\%$ 
and $14\%$, respectively. Spectrum softening for these fueling cases 
positively affects the \gls{FTC} magnitude, and this effect seems to be 
proportional to the spectrum shift.

@@

\subsection{Six factor analysis}
The effective multiplication factor can be expressed as follows:
\begin{align}
k_{eff} &= \eta f p \epsilon P_f P_t
\intertext{where}
\eta     &= \mbox{neutron reproduction factor} \nonumber \\
f        &= \mbox{thermal utilization factor} \nonumber \\
p        &= \mbox{resonance escape probability} \nonumber \\
\epsilon &= \mbox{fast fission factor} \nonumber \\
P_f      &= \mbox{fast non-leakage probability} \nonumber \\
P_t      &= \mbox{thermal non-leakage probability.} \nonumber
\end{align}

Table~\ref{tab:six_factor} summarizes the six factor for 3 different initial 
fuel salt compositions at startup and equilibrium. By using SERPENT-2 built-in 
online reprocessing capabilities, six factor is calculated at the 
beginning of the operation and after 30 years of operation. Neutron population 
and number of active/inactive cycles were selected to obtain $k_{eff}$ 
statistical uncertainty less than 12 pcm. The fast and thermal non-leakage 
probabilities remain constant regardless of initial fissile material and 
neutron spectrum shift during operation. The thermal utilization factor (f) 
remains almost constant during operation for the $^{233}$U and TRU cases but 
considerably declines for the Pu case due to significant neutron spectrum 
softening.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} [ht!]
	\caption{Six factor for the SD-TMSR model for 3 different initial 
		fuel salt compositions at startup and equilibrium.}
	\begin{tabularx}{\textwidth}{ X | X X  X X  X X | p{0.1\textwidth}} \hline
		\multirow{3}{*}{Factor}  & \multicolumn{6}{c|}{Startup fissile 
			material} & \multirow{3}{*}{$\pm\bar{\sigma}$} \\ 
			\cline{2-7}
		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
		\multicolumn{2}{c|}{TRU} \\ \cline{2-7}
		\space  & Initial & Equil & Initial & Equil & Initial & Equil & \space 
		\\ \hline
		$\eta$  & 1.26 & 1.40 & 1.66 & 1.44 & 1.59 & 1.31&4.9E-4\\ 
		f       & 0.97 & 0.98 & 0.96 & 0.76 & 0.80 & 0.75&2.1E-4 \\
		p       & 0.54 & 0.43 & 0.26 & 0.16 & 0.17 & 0.15&4.6E-4 \\
		$\epsilon$ & 1.49 & 1.67 & 2.45 & 5.87 & 4.83 & 6.81&6.2E-4 \\
		P$_f$   & 0.99 & 0.99 & 0.99 & 0.99& 0.99 & 0.99&1.7E-6 \\
		P$_t$   & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00&6.5E-11 \\ \hline
	\end{tabularx}
	\label{tab:six_factor}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In contrast, the neutron reproduction factor ($\eta$), resonance escape 
probability ($p$), and fast fission factor ($\epsilon$) differ notably between 
the initial and equilibrium state for all three initial fissile materials.  
$\epsilon$ is much larger at startup for the Pu and TRU cases because these 
initial fissile materials provide a much harder neutron spectrum than 
$^{233}$U, and $\epsilon$ grows throughout the core's lifetime. Conversely, 
$p$ decreases during reactor operation. The neutron reproduction factor ($\eta$)  
increases during reactor operation for the $^{233}$U as initial fuel due to 
the accumulation of fissile plutonium isotopes, which produce more neutrons 
per fission ($\nu$). The other two scenarios demonstrate opposite behavior: 
plutonium isotopes with large $\nu$ are gradually substituted with $^{233}$U, 
which has a lower $\nu$ \cite{sjostrand_cross_1960}. This six factors' 
evolution agrees with previously determined evolution parameters for a similar 
single-fluid double-zone \gls{MSBR} \cite{ashraf2019whole_core, 
rykhlevskii2019modeling, park_whole_2015}.

>>>>

\subsection{Neutron flux}
Figures~\ref{fig:fast_flux} and \ref{fig:thermal_flux} show the radial 
distribution of fast (energy range between 0.625 eV and 20 MeV) and thermal 
(energy range between 10$^{-5}$ eV and 0.625 eV) neutron flux for three 
different initial fissile materials in the fuel salt ($^{233}$U, reactor-grade 
Pu, TRU) at startup and at equilibrium (after $\approx 30$ years of 
operation). Actinides' evolution and poisonous fission product accumulation 
for various initial fissile compositions demonstrates the different effects on 
the SD-TMSR neutronics performance. For the $^{233}$U case, the thermal 
neutron flux is suppressed at equilibrium because fissile $^{233}$U in the 
core is being substituted with heavier fissile actinides: $^{235}$U, 
$^{239}$Pu, and $^{241}$Pu. This agrees with results in literature 
\cite{rykhlevskii2019modeling, ashraf2019whole_core}.
\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
	\includegraphics[width=\textwidth]{radial_fast_flux_init_vs_eq.png} 
	\caption{Radial fast neutron flux distribution for 3 different initial 
		fuel salt compositions at startup and equilibrium (the fast flux 
		confidence interval $\pm\sigma<2.5$\% for all cases).}
	\label{fig:fast_flux}
\end{figure}
\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
	\includegraphics[width=\textwidth]{radial_thermal_flux_init_vs_eq.png} 
	\caption{Radial thermal neutron flux distribution for 3 different initial 
		fuel salt compositions at startup and equilibrium (the thermal flux 
		confidence interval $\pm\sigma<1.6$\% for all cases).}
	\label{fig:thermal_flux}
\end{figure}

Opposite behavior is observed for the reactor-grade Pu and TRU cases. For  
these cases, the thermal neutron flux increases during operation while fast 
neutron flux decreases. Fissile Pu nuclides (generate relatively hard 
spectrum) from initial fuel salt composition are gradually substituted with  
$^{233}$U (generates relatively soft spectrum), produced from fertile 
$^{232}$Th. During reactor operation, $^{233}$U becomes the primary fissile 
isotope, which softening the neutron spectrum of the reactor.

Notably, the neutron flux change for both the fast and thermal energies is 
much larger for the reactor-grade Pu case than for TRU case 
(Figures~\ref{fig:fast_flux} and \ref{fig:thermal_flux}). The reason is the 
much softer neutron spectrum for the TRU initial loading compared with the 
reactor-grade Pu as shown in Figure~\ref{fig:spectrumFLUX110vC}: peak thermal 
neutron flux is about 4 times larger for the TRU case. The neutron spectrum in 
the SD-TMSR core initially loaded by TRU is much softer than the reactor-grade 
Pu case and even than the U-233 case because $^{232}$Th inventory is the 
lowest for the TRU case: 54.4t instead of 67.5t  and 76.9t for the  
reactor-grade Pu and U-233 cases, respectively (Table~\ref{tab:table5}). 
$^{232}$Th greatly affects the neutron energy spectrum due to its large 
absorption cross section in the thermal energy range and resonance region 
between $10^{-5}$ and $10^{-3}$. Finally, when the TRU and the reactor-grade 
Pu cases reached equilibrium fuel salt composition ($\approx 30$ years after 
startup), the radial fast and thermal neutron flux distribution became similar 
in both shape and magnitude.

More changes in thermal neutron flux shape and magnitude during the reactor 
operation for the $^{233}$U case are observed in the inner core zone 
($R\lesssim150$) than in the outer core zone. In the outer core zone, 
significant changes during reactor operation are observed for the thermal 
neutron flux for the reactor-grade Pu case. In contrast, for the TRU case, it 
is almost negligible. Additionally, Figure~\ref{fig:thermal_flux} shows 
relatively significant changes in thermal flux leakage from the core for the 
Pu (equilibrium composition) and TRU (initial and equilibrium composition) 
cases. The SD-TMSR core design was optimized for $^{233}$U  
\cite{li_optimization_2018}; thus, the core geometry (e.g., channels lattice 
pitch) must be re-optimized for another type of fuel to obtain better 
neutronics performance.

@@

The \gls{FTC} is negative for all considered fuel compositions due to thermal 
Doppler broadening of the resonance capture cross sections in the thorium. For 
the $^{233}$U case, the \gls{FTC} decreases in magnitude by $25\%$ due to 
neutron spectrum hardening during the reactor operation. For reactor-grade Pu 
and TRU cases, the \gls{FTC} increases in magnitude at equilibrium, by $31\%$ 
and $14\%$, respectively.

The \gls{FTC} is a combination of the Doppler effect coefficient 
($\alpha_{D,F}$) and density coefficient ($\alpha_{\rho,F}$) and significantly 
affected by the neutron spectrum. Li \emph{et al.} reported that 
$\alpha_{D,F}$ in thermal \gls{MSR} is always negative and increases by 
magnitude when spectrum hardening (see Table~\ref{tab:tcoe}, first raw). 
In contrast, $\alpha_{\rho,F}$ is a combination of moderator-to-fuel volume 
ratio, absorption cross section of heavy metal, and the core leakage. When the 
fuel salt temperature increases, the salt becomes less dense, causing a 
reduction in the fuel concentration and the neutron spectrum become softer. 
Such spectrum softening is leading to a rise in macroscopic absorption cross 
section of the fissile isotopes. Moreover, the spectrum softening may leads to 
a larger fast fission reaction rate \cite{li_effects_2018-1}. Thus, spectrum 
softening positively affects the density coefficient ($\alpha_{\rho,F}$): 
$+1.54$ $pcm/K$ and $-1.58$ $pcm/K$ at the startup and equilibrium for the 
reactor-grade Pu case, respectively. More discussion about effects of fuel 
salt composition in the \gls{FTC} can be found elsewhere 
\cite{li_effects_2018-1}.

@@
